Tidy data structure to support exploration and modeling of temporal data

### 2018-12-06 main.Rmd
added "respect structural missingness" into conclusion

<!--
## Time series of nested and crossed factors

A collection of time series can often be intrinsically arranged along multivariate data of nested and crossed factors, which is also known as hierarchical and grouped time series [@fpp]. For example, from an operational point of view, a manufacturer can add up every store’s sales by region, by state, and by country along a geographical tree; alternatively, one can group the sales for each product together based on common attributes such as store, brand, price range and so forth, resulting in a non-hierarchical structure. The former gives an example of hierarchical time series, and the latter shows grouped time series. And even when collections of time series are absent from hierarchical structure, it is possible to arrange them empirically into a hierarchy such as regression tree [@sankaran_interactive_2017].

The R package **hts** [@R-hts] is the implementation of structured collections of time series, and provides tools for visualizing, analyzing, and forecasting such data. But it is a pain to configure node list or grouping matrix as the increase in hierarchic depth and grouping factors. This is resulted from the fact that the structure specification is separated from data itself and represented numerically, which is rather counterintuitive from the user's perspective.
-->

@@

Not only pinpoints a "key" observational units in the tsibble but also provides a solution to seamlessly link between the data, models, and forecasts. This neatly separates the data from models and forecasts, leaving more room for compulsory model components, such as coefficients, fitted values and residuals. More details are given in the following section.

@@

Sensors have been put up to collect data for the project of smart city across major cities in Australia. One of the trials is monitoring households' electricity usage through installed smart meters in the area of New Castle over 2010--2014 [@smart-meter]. Year 2013 has been sliced to examine temporal patterns of customer's energy consumption with **tsibble** in this paper. Half-hourly general supply in kwH have been recored for `r format(tsibble::n_keys(elec_ts), big.mark = ",")` customers in the data set, resulting in `r format(NROW(elec_ts), big.mark = ",")` observations in total. Customer's demographic data provides explanatory variables other than time in a separate data table. Two data tables might be joined to explore different sources that contribute to daily electricity use when needed.

@@

>>>>

@@

Not only pinpoints a "key" observational units in the tsibble but also provides a solution to seamlessly link between the data, models, and forecasts. This neatly decouples the data from models and forecasts, leaving more room for compulsory model components, such as coefficients, fitted values and residuals. More details are given in the following section.

@@

Sensors have been put up to collect data for the project of smart city across major cities in Australia. One of the trials is monitoring households' electricity usage through installed smart meters in the area of New Castle over 2010--2014 [@smart-meter]. Year 2013 has been sliced to examine temporal patterns of customer's energy consumption with **tsibble** in this paper. Half-hourly general supply in kwH have been recored for `r format(tsibble::n_keys(elec_ts), big.mark = ",")` customers in the data set, resulting in `r format(NROW(elec_ts), big.mark = ",")` observations in total. Customer's demographic data provides explanatory variables other than time in a different data table. Two data tables might be joined to explore different sources that contribute to daily electricity use when needed.

@@

A missing piece of the *tsibble* data is to enable user-defined calendars and respect structural missing observations. For example, a call center operates only between 9:00am and 5:00pm on week days and stock trading resumes on Monday straight after Friday. No data available outside trading hours would be labelled as structural missingess, which *tsibble* currently disregards. However, few R packages provide functionality to create and manage many sorts of calendars, including market-specific business calendar. This delays the implementation. Generally, custom calendars would be easily embedded into the tsibble framework. Consequently these tsibble operators, like `fill_gaps()`, would work out of box; forecasts would be generated within its definable time range.
